	\experienceItem{Engineering Manager}{OSIsoft, LLC., San Leandro, CA}{Jan 2016 -- present}
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Currently manage a team working on distributed PaaS and SaaS \href{https://bit.ly/2FZfzED}{metadata solutions} for streaming data to enable asset management using context. Also maintaining an on-prem \href{https://bit.ly/2B6bvPX}{event notifications product}. Manage dependencies across multiple teams and guide team with design and architecture decisions. Work with stakeholders to manage backlog and drive road-map. Responsible for hiring, mentoring developers, performance reviews, 1-1's, sprint velocity and overall team health.}
	\resumeListItem{Started new team/project on enterprise wide IoT data collection. Interviewed candidates for hiring into the team. Gathered requirements and defined product direction in collaboration with product manager and group lead. Motivated use of Git as source control. Developed an administration API with back-end and front-end. Developed a logging infrastructure. Architected mechanism for high-throughput streaming data egress from IoT module to enterprise storage solutions.}
	\resumeListItem{Managed a team working on a cloud-native \href{https://bit.ly/2FZfzED}{distributed Sequential Data Store} PaaS solution to process billions of streams from millions of devices, both real-time and historical. Collaborated with customers, product managers and engineering architect to identify requirements, define system design and develop road-map. Recruited and on-boarded developers into team. Took project from prototype to product. Assisted team members with sprint tasks and helped them complete goals. Created high value product team that led to vNext series of enterprise solutions. Developed a caching service - passed on to developers in the team. Managed SDLC. Introduced CI/CD. Researched partner technologies and provided \href{https://bit.ly/2DwSLe4}{feedback}. Presented at meetings and conferences.}
	\resumeItemListEnd