\experienceItem{Engineering Manager}{OSIsoft, LLC., San Leandro, CA}{Jan 2016 -- Jan 2020}


\experienceSubItem{PaaS, SaaS Product (Metadata Solution)}{Feb 2019 - Jan 2020}[https://bit.ly/2FZfzED]
\resumeItemListStart
\resumeListItem {Managed and grew a team working on large-scale distributed Platform-as-a-Service (PaaS) and Software-as-a-Service (SaaS) metadata solutions for storage and analysis of high-throughput streaming process data to enable asset management using context for industrial applications. Context involves models, hierarchies, objects, for equipment and data, as a single repository.}
\resumeListItem {Led team through successful completion of program for enabling data science on streaming data by automated generation of metadata using rules.}
\resumeListItem {Responsible for hiring, mentoring developers, performance reviews, 1-1's, sprint velocity and overall team health.}
\resumeListItem {Product owner. Worked closely with cross-functional stakeholders (Product and Program Managers, Architects) to manage product backlog and drive road-map.}
\resumeListItem {Managed dependencies across multiple teams and guided the team with design and architecture decisions.}
\resumeItemListEnd

\experienceSubItem{Event Notifications Product}{Feb 2019 - Jan 2020}[https://bit.ly/3uNi84j]
\resumeItemListStart
\resumeListItem {Worked with product manager to roll out fixes on an as-needed basis and managed developer escalation.}
\resumeItemListEnd

\experienceSubItem{IoT Product}{May 2017 - Jan 2019}[https://bit.ly/3nOpaS0]

\resumeItemListStart
\resumeListItem {Started new team for \href{https://bit.ly/3af97rd}{project} on large-scale, enterprise-wide, high-throughput streaming data collection from IoT devices. Interviewed candidates for hiring into the team. Gathered requirements and defined product direction in collaboration with product management, group lead and customers.}
\resumeListItem {Motivated using Git for source control. Developed an administration API with back-end and front-end. Developed a logging infrastructure. Developed mechanism for high-throughput streaming data egress from IoT module to enterprise data storage solutions for both real-time and historical data.}
\resumeItemListEnd

\experienceSubItem{PaaS Product (Storage Solution; Core Platform and Infrastructure)}{Jan 2016 - April 2017}[https://bit.ly/2FZfzED]

\resumeItemListStart
\resumeListItem {Founded and grew a team of software developers working on multi-tenant distributed Platform-as-a-Service (PaaS) solution. Recruited and on-boarded developers into team. Drove software engineering best practices, including agile methodologies. Took project from prototype to product. Ran sprints, assisted developers with tasks and enabled team to accomplised goals. Developed a caching service - passed on to developers in the team. Created a high-value engineering team that developed high-visibility, large-scale distributed data platform product which spawned next-generation series of enterprise software solutions.}
\resumeListItem {Defined system architecture for a cloud-native distributed Sequential Data Store PaaS solution to ingest, process, store, analyze, query, share billions of (real-time and historical) streams from millions of industrial devices and Internet-of-Things (IoT) sensors. Collaborated cross-functionally with customers, product managers and engineering architect to identify requirements and develop road-map.}
\resumeListItem {Managed all aspects of the Software Development Life Cycle (SDLC). Introduced CI/CD. Researched new partner technologies and provided \href{https://bit.ly/2DwSLe4}{feedback}. Presented at meetings and conferences.}
\resumeItemListEnd