\experienceItem{Software Engineering Team Leader}{OSIsoft, LLC., San Leandro, CA}{Jan 2016 -- present}

\experienceSubItem{IoT Product}{}%May 2017 - Jan 2019

\resumeItemListStart
\resumeListItem {Started new team/project on enterprise wide IoT data collection. Interviewed candidates for hiring into the team. Gathered requirements and defined product direction in collaboration with product management and group lead.}
\resumeListItem {Migrated legacy source control to Git. Developed an administration API with back-end and front-end. Developed a logging infrastructure. Developed mechanism for data egress from IoT module to enterprise storage solutions.}
\resumeItemListEnd

\experienceSubItem{SaaS Product}{}[https://bit.ly/2FZfzED]%Jan 2016 - April 2017

\resumeItemListStart
\resumeListItem {Managed (using Agile processes) a team of software developers working on distributed enterprise scale SaaS product.}
\resumeListItem {Defined system architecture for a distributed sequential data store to process billions of streams. Collaborated with customers, product managers to identify requirements and develop road-map. Managed SDLC. Introduced CI/CD. Researched new partner technologies and provided feedback [\href{https://bit.ly/2DwSLe4}{bit.ly/2DwSLe4}]. Presented at meetings, conferences.}
\resumeListItem {Recruited and on-boarded developers into team. Assisted team members with sprint tasks and helped them complete goals. Developed a caching service - passed on to developers in the team.}
\resumeItemListEnd