\experienceItem{Software Developer}{OSIsoft, LLC., San Leandro, CA}{May 2011 -- Jan 2015}
	
\experienceSubItem{PaaS, SaaS R\&D Project (Storage Solution; Core Platform and Infrastructure)}{June 2014 - Jan 2015}[https://bit.ly/2FZfzED]

\resumeItemListStart
\resumeListItem {Founding team member and lead developer in charge of creating core platform, infrastructure for distributed streaming-data Platform-as-a-Service (PaaS) and Software-as-a-Service (SaaS) solutions.} 
\resumeListItem {Developed components of multi-tenant distributed data store.}
\resumeListItem {Added data replication functionality leveraging leader-election and distributed consensus algorithms.}
\resumeListItem {Developed automated multi-threaded chaos tests. Created standards for DevOps -  passed on to other engineers.}
\resumeListItem {Mentored new engineer in developing a real-time health monitoring framework.}
\resumeItemListEnd

\experienceSubItem{SaaS Product}{Feb 2013 - June 2014}[https://bit.ly/2B0dPYM]

\resumeItemListStart
\resumeListItem {Part of team that developed first cloud product at OSIsoft.}
\resumeListItem {Developed front-end and back-end components of cloud-based enterprise SaaS product for process data transfers.}
\resumeListItem {Developed secure RESTful APIs. Did threat modeling of cloud services and corresponding on-prem components.}
\resumeListItem {Architected and developed an alarm infrastructure and a cloud-based software delivery and auto-update system.}
\resumeListItem {Enhanced SQL database schema and developed full stack from server-side data-access layer to client-side APIs.}
\resumeListItem {Developed DevOps tools and data-mining queries for reporting on health statuses of multi-tenant cloud application.}
\resumeListItem {Developed multi-layered modular and scalable WPF applications.}
\resumeListItem {Consistently delivered committed items in fast-paced, quick turn-around, scrum-based development cycles. Led knowledge transfer sessions to handover work to new team member(s) while transitioning to a R\&D project.}
\resumeItemListEnd

\experienceSubItem{Middleware Product}{May 2011 - Feb 2013}[https://bit.ly/2MwOVoc]

\resumeItemListStart
\resumeListItem {Developed and maintained test automation frameworks. Developed and maintained software delivery systems using Wise and WiX. Enhanced and maintained codebase (specifically data buffering) for core middleware.} \resumeListItem  {Worked with uses in Fortune 500 companies through multiple successful releases.}
\resumeItemListEnd