% Copyright (c) 2024 Manas Talukdar
% 
% This software is released under the MIT License.
% https://opensource.org/licenses/MIT

\vspace{2pt}
\resumeItemListStart
\resumeListItem {\textbf{International Business Award (Stevie). Innovator of the Year - Issued by International Business Awards®, August 2024.} \textit{Manas Talukdar has been honored with a Gold Stevie® Award as "Innovator of the Year" in the "Management" category in The 21st Annual \href{https://stevieawards.com/iba}{International Business Awards®} for "Innovations and Leadership in AI and Data".}}
\resumeListItem {\textbf{Globee Award for Technology. Professional of the Year | Artificial Intelligence - Issued by Globee Business Awards, June 2024.} \textit{Manas Talukdar was recognized with a Globee Award for Technology in the category of "Artificial Intelligence Achievement of the Year", for \href{https://credential.globeeawards.com/6ed11155-4a6c-4b9f-8987-3758196b5319\#gs.behnfb}{Innovative product development in AI with patents and wide adoption}. This recognition underscores the entrant's distinguished performance, creativity, and impact within their sector, highlighting them as high achievers.}}
\resumeListItem {\textbf{Globee Award for Technology. Artificial Intelligence Achievement of the Year - Issued by Globee Business Awards, June 2024.} \textit{Manas Talukdar was recognized with a \href{https://globeeawards.com/technology/}{Globee Award for Technology} in the category of "Artificial Intelligence Achievement of the Year", for \href{https://credential.globeeawards.com/dcc25d00-6d28-4706-bad2-c9727ec0725b\#gs.behk3u}{Innovative product development in AI with patents and wide adoption}. This recognition underscores the entrant's distinguished performance, creativity, and impact within their sector, highlighting them as high achievers.}}
\resumeListItem {\textbf{Titan Business Award. Issued by Titan Awards, May 2024.} \textit{Manas Talukdar was recognized with a 2024 Titan Business Award in the category of "Executives \& Professionals - Innovator of the Year" for \href{https://thetitanawards.com/winner-info.php?id=3772}{leadership and innovations in AI with patents and adoption}.}}
\resumeListItem {\textbf{Global Recognition Award. Issued by Global Recognition Awards, March 2024.} \textit{Manas Talukdar has been recognized with a \href{https://globalrecognitionawards.org/winners/2024/manas-talukdar-wins-2024-global-recognition-award/}{2024 Global Recognition Award} for his exceptional contributions and achievements in the field of artificial intelligence and large-scale data infrastructure.}}
\resumeListItem {\textbf{Indian Achiever's Award. Issued by Indian Achievers' Forum, March 2024.} \textit{We extend our heartfelt congratulations to Mr. Manas Talukdar for receiving the prestigious \href{https://www.iafindia.com/mr-manas-talukdar/}{Indian Achievers' Award 2023-24}. This recognition is a testament to his outstanding achievements and remarkable contributions towards Science \& Technology.}}
\resumeItemListEnd