% Copyright (c) 2024 Manas Talukdar
% 
% This software is released under the MIT License.
% https://opensource.org/licenses/MIT

\textbf{Honors}\vspace{-8pt}
\resumeItemListStart
\resumeListItem{Invited to be an Ambassador at the AI Frontier Network, May 2024. \textit{The AI Frontier Network (AIFN) invites renowned thought leaders and change makers to join as Ambassadors, catalyzing the artificial intelligence revolution. This select group have distinguished themselves as leaders and innovators pioneering new frontiers in the age of AI.}}
\resumeListItem{IEEE Senior Membership. Issued by IEEE, August 2023. \textit{IEEE senior membership requires extensive experience and reflects professional maturity. It is based on a detailed scrutiny of documented and sustained achievements and is bestowed only to those who have consistently made significant contributions to the profession.}}
\resumeListItem {Successfully completed a 5-year diploma from \href{https://afacs.in/}{\textbf{Assam Fine Arts and Crafts Society}}, India.}
\resumeListItem {Performance in Science and Mathematics in All India Secondary School Examination in the top 1/8th.}
\resumeListItem {Successfully qualified in All-India Mathematics Olympiad conducted by Delhi Association of Mathematics Teachers.}
\resumeItemListEnd

\textbf{Awards}\vspace{-8pt}
\resumeItemListStart
\resumeListItem {\textbf{Globee Award for Technology. Professional of the Year | Artificial Intelligence - Issued by Globee Business Awards, June 2024.} \textit{Manas Talukdar was recognized with a Globee Award for Technology in the category of “Artificial Intelligence Achievement of the Year”, for \href{https://credential.globeeawards.com/6ed11155-4a6c-4b9f-8987-3758196b5319#gs.behnfb}{Innovative product development in AI with patents and wide adoption}. This recognition underscores the entrant's distinguished performance, creativity, and impact within their sector, highlighting them as high achievers.}}
\resumeListItem {\textbf{Globee Award for Technology. Artificial Intelligence Achievement of the Year - Issued by Globee Business Awards, June 2024.} \textit{Manas Talukdar was recognized with a \href{https://globeeawards.com/technology/}{Globee Award for Technology} in the category of “Artificial Intelligence Achievement of the Year”, for \href{https://credential.globeeawards.com/dcc25d00-6d28-4706-bad2-c9727ec0725b#gs.behk3u}{Innovative product development in AI with patents and wide adoption}. This recognition underscores the entrant’s distinguished performance, creativity, and impact within their sector, highlighting them as high achievers.}}
\resumeListItem {\textbf{Titan Business Award. Issued by Titan Awards, May 2024.} \textit{Manas Talukdar was recognized with a 2024 Titan Business Award in the category of “Executives & Professionals - Innovator of the Year” for \href{https://thetitanawards.com/winner-info.php?id=3772}{leadership and innovations in AI with patents and adoption}.}}
\resumeListItem {\textbf{Global Recognition Award. Issued by Global Recognition Awards, March 2024.} \textit{Manas Talukdar has been recognized with a \href{https://globalrecognitionawards.org/winners/2024/manas-talukdar-wins-2024-global-recognition-award/}{2024 Global Recognition Award} for his exceptional contributions and achievements in the field of artificial intelligence and large-scale data infrastructure.}}
\resumeListItem {\textbf{Indian Achiever's Award. Issued by Indian Achievers’ Forum, March 2024.} \textit{We extend our heartfelt congratulations to Mr. Manas Talukdar for receiving the prestigious \href{https://www.iafindia.com/mr-manas-talukdar/}{Indian Achievers’ Award 2023-24}. This recognition is a testament to his outstanding achievements and remarkable contributions towards Science & Technology.}}
\resumeItemListEnd