% Copyright (c) 2024 Manas Talukdar
% 
% This software is released under the MIT License.
% https://opensource.org/licenses/MIT

\vspace{2pt}
\resumeItemListStart
\resumeListItem{
	\textbf{Invited to be a member of the Forbes Technology Council, February 2025.}
	\begin{shadequote}{}
		\href{https://www.forbes.com/councils/forbestechcouncil/}{Forbes Technology Council} is an invitation-only, fee-based organization comprised of leading CIOs, CTOs and technology executives.
	\end{shadequote}
	\begin{shadequote}{}
		Members of \href{https://councils.forbes.com/forbestechcouncil}{Forbes Technology Council} are respected technology leaders selected for the Council for their depth and diversity of experience.
		...
		Eligible applicants are vetted by our selection committee, and if approved, are invited...
		Examples of Forbes Technology Council members include founders, partners, and CEOs of technology companies, C-level technology executives such as CTOs and CIOs, and VPs of technology teams.
	\end{shadequote}
	\begin{shadequote}{}
		\href{https://www.linkedin.com/company/forbestechcouncil/about/}{Forbes Technology Council} is a vetted professional networking community for leading CIOs, CTOs and senior technology executives.
	\end{shadequote}
}
\resumeListItem{
	\textbf{Fellow of the British Computer Society (BCS). Issued by British Computer Society (BCS), February 2025.}
	\begin{shadequote}{}
		\href{https://www.bcs.org/membership-and-registrations/become-a-member/bcs-fellowship/}{BCS Fellowship} is home to the most influential professionals in the digital industry.
	\end{shadequote}
	\begin{shadequote}{}
		Suitable for: Inspirational technology leaders, innovators and academics.
	\end{shadequote}
	\begin{shadequote}{}
	...recognition you’ve earned as a pioneer of the modern profession. ...extending your influence as a thought leader and for giving back to the industry with opportunities for policy formation, education, public engagement and more.
	\end{shadequote}
}
\resumeListItem{
	\textbf{Invited to be listed in Marquis Who’s Who, July 2024.}
	\begin{shadequote}{}
		\href{https://marquiswhoswho.com/}{Marquis Who’s Who} was established in 1898 and promptly began publishing biographical data in 1899. More than 125 years ago, our founder, Albert Nelson Marquis, established a standard of excellence with the first publication of Who’s Who in America.
	\end{shadequote}
	\begin{shadequote}{}
		A biographical dictionary of notable men and women, first published in 1899 which highlights thousands of biographies that reach beyond lists and facts to shed additional light on what makes these inspiring individuals who they are. Among our listees are Nobel and Pulitzer Prize winners, legendary athletes, best-selling authors, accomplished artists, renowned entertainers, entrepreneurs, corporate executives, and more.
	\end{shadequote}
}
\resumeListItem{
	\textbf{Invited to be a member of the American Society for AI (ASFAI), July 2024.} \begin{shadequote}{}\href{https://www.asfai.org/}{American Society for Artificial Intelligence} (ASFAI) is a private \& prestigious club that brings together prominent leaders \& executives. … Membership is reserved for established leaders and executives, C-Suite and Senior-level, and includes a robust vetting process and with Board approval. Members are of diverse backgrounds and industries; including pioneers in AI, entrepreneurs, executives, technologists, philanthropists, authors, investors, lawyers, policymakers, researchers, computer scientists, engineers, doctors, and professors.\end{shadequote}
}
\resumeListItem{
	\textbf{Invited to be an Ambassador at the AI Frontier Network, May 2024.}
	\begin{shadequote}{}The \href{https://aifn.co/}{AI Frontier Network} (AIFN) invites renowned thought leaders and change makers to join as Ambassadors, catalyzing the artificial intelligence revolution. This select group have distinguished themselves as leaders and innovators pioneering new frontiers in the age of AI.\end{shadequote}
	\begin{shadequote}{}AIFN Ambassadors are members who have distinguished themselves as leaders and innovators pioneering new frontiers in the age of AI. The group includes CEOs, entrepreneurs, authors, speakers, engineers, and tech leaders driving innovation… They bring a wealth of expertise and vision from their roles, driving growth and collaboration within the AI Frontier Network.\end{shadequote}
}
\resumeListItem{\textbf{IEEE Senior Membership. Issued by IEEE, August 2023.} \textit{IEEE senior membership requires extensive experience and reflects professional maturity. It is based on a detailed scrutiny of documented and sustained achievements and is bestowed only to those who have consistently made significant contributions to the profession.}}
\resumeListItem {Successfully completed a 5-year diploma from \href{https://afacs.in/}{\textbf{Assam Fine Arts and Crafts Society}}, India.}
\resumeListItem {Performance in Science and Mathematics in All India Secondary School Examination in the top 1/8th.}
\resumeListItem {Successfully qualified in All-India Mathematics Olympiad conducted by Delhi Association of Mathematics Teachers.}
\resumeItemListEnd