\documentclass[letterpaper,10pt]{article}

\usepackage[english]{babel}
%\usepackage[T1]{fontenc} % needed for pipe character
\usepackage[empty]{fullpage}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[margin=0.5in]{geometry} % setting margins
\usepackage{lmodern} % font
\usepackage{fontawesome}
\usepackage{titlesec} % section formatting
\usepackage[usenames,dvipsnames]{color} % section formatting
%\usepackage{pgffor}
%\usepackage{xifthen}
\usepackage{xparse}

% https://latex.org/forum/viewtopic.php?t=5842
\hyphenpenalty 10000
\exhyphenpenalty 10000

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\title{Manas Talukdar}
\author{Manas Talukdar}
\date{\today}

%\hypersetup{
%	colorlinks=true,
%	linkcolor=blue,
%	filecolor=magenta,  
%	urlcolor=cyan,   
%%	urlcolor=[rgb]{0.0, 0.5, 1.0}, % http://latexcolor.com/
%}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\fancyfoot[C, C]{
	\begin{tabular}{c | c}
		Manas Talukdar\enspace & \enspace \thepage \\
	\end{tabular}
}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\NewDocumentCommand{\educationItem}{mmmom}{
	\IfNoValueTF{#4}
		{ \textbf{#1}, #2, \textit{#3} & #5 \\ }
		{ \textbf{#1}, #2, \textit{#3}, {\small #4} & #5 \\ }
}

\newcommand{\experienceItem}[3]{
	\begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}}c}
		\multicolumn{1}{l}{\textbf{#1}, #2} & \multicolumn{1}{r}{#3}\\
	\end{tabular*}\vspace{-10pt}
}

\ExplSyntaxOn
\NewDocumentCommand{\experienceSubItem}{mmo}{
	\tl_if_empty:nTF{#2} 
	{
		\IfNoValueTF{#3} 
		{ \textit{#1}\vspace{-8pt} }
		{ \textit{#1\enspace[\href{#3}{#3}]}\vspace{-8pt} }
	}
	{
		\IfNoValueTF{#3} 
		{ \textit{#1\enspace(#2)}\vspace{-8pt} }
		{ \textit{#1\enspace(#2)\enspace[\href{#3}{#3}]}\vspace{-8pt} }
	}
}
\ExplSyntaxOff

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeListItem}[1]{
	\item{#1 \vspace{-6pt}}
}

%-------------------------------------------
%%%%%%  Resume content starts here  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}\thispagestyle{empty}
	
	%----------Heading-----------------
	\begin{center}
		\begin{tabular}{c | c | c}			
			\multicolumn{3}{c}{\textbf{\LARGE MANAS TALUKDAR}} \\[2mm]
			\faMobile\enspace(xxx)-xxx-xxxx \enspace & \enspace \faEnvelopeO\enspace\href{mailto:firstName.lastName@gmail.com}{firstName.lastName@gmail.com} \enspace & \enspace \faLinkedin\enspace\href{https://www.linkedin.com/in/manastalukdar}{linkedin.com/in/manastalukdar} \\ 
		\end{tabular}
	\end{center}

	%-----------Summary-----------------
	{\fontfamily{qtm}\selectfont
	\textit{Engineering manager experienced in hiring, mentoring software engineers and building and running a team. Excellent communication skills with experience in collaborating with users, executive leadership, product management and customer support. Over 10 years of software development experience with middleware, web services, cloud computing, distributed systems and IoT products. Quick learner, self-driven with proven track record in delivering projects that involved learning new technologies. Current core competencies in large scale system design and people management.}
	}

	%-----------Education-----------------
	\section{Education}	
	
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\educationItem
		{North Carolina State University}{Raleigh, NC}{Master of Science, Electrical Engineering}{2005 -- May 2007}
		\educationItem
		{Gauhati University}{Assam, India}{Bachelor of Engg., Electrical Engg.}[Dean's List - 5 semesters]{Aug 2000 -- June 2004}		
	\end{tabular*}

	%-----------Experience-----------------
	\section{Experience}
	
	\experienceItem{Software Engineering Team Leader}{OSIsoft, LLC., San Leandro, CA}{Jan 2016 -- present}

	\experienceSubItem{IoT Product}{May 2017 -- present}
	
	\resumeItemListStart
	\resumeListItem {Started new team/project on enterprise wide IoT data collection. Interviewed candidates for hiring into the team. Gathered requirements and defined product direction in collaboration with product management and group lead.}
	\resumeListItem {Migrated legacy source control to Git. Developed an administration API with back-end and front-end. Developed a logging infrastructure. Developed mechanism for data egress from IoT module to enterprise storage solutions.}
	\resumeItemListEnd

	\experienceSubItem{SaaS Product}{Jan 2016 - April 2017}[https://bit.ly/2HUbQKb]
	
	\resumeItemListStart
	\resumeListItem {Managed (using Agile processes) a team of software developers working on distributed enterprise scale SaaS product.}
	\resumeListItem {Defined system architecture for a distributed sequential data store to process billions of streams. Collaborated with customers, product managers to identify requirements and develop road-map. Managed SDLC. Introduced CI. Researched new partner technologies and provided feedback [\href{https://bit.ly/2Hy2gfU}{bit.ly/2Hy2gfU}]. Presented at meetings and conferences.}
	\resumeListItem {Recruited and on-boarded developers into team. Assisted team members with sprint tasks and helped them complete goals. Developed a caching service - passed on to developers in the team.}
	\resumeItemListEnd

	\experienceItem{Senior Software Developer}{OSIsoft, LLC., San Leandro, CA}{Feb 2015 -- Jan 2016}
	
	\experienceSubItem{SaaS Product}{}[https://bit.ly/2HUbQKb]
	
	\resumeItemListStart
	\resumeListItem {Architected and developed distributed micro-services using new cloud technology -- Service Fabric [\href{https://bit.ly/2r5hSxY}{bit.ly/2r5hSxY}].}
	\resumeListItem {Security champion for team. Threat modeled components and data flow in the project and led review sessions.}
	\resumeListItem {Architected full-stack real-time health monitoring and logging system with data access and client APIs.}
	\resumeListItem {Interviewed, on-boarded and mentored new engineers in project.}
	\resumeItemListEnd

	\experienceItem{Software Developer}{OSIsoft, LLC., San Leandro, CA}{May 2011 -- Jan 2015}
	
	\experienceSubItem{SaaS R\&D Project}{June 2014 - Jan 2015}[https://bit.ly/2HUbQKb]

	\resumeItemListStart
	\resumeListItem {Developed components of multi-tenant SaaS product for process data storage. Added data replication. Developed automated multi-threaded chaos tests. Developed, documented standards for DevOps -  passed on to other engineers.}
	\resumeListItem {Mentored new engineer in developing a real-time health monitoring framework.}
	\resumeItemListEnd

	\experienceSubItem{SaaS Product}{Feb 2013 - June 2014}[https://bit.ly/2r4i9jV]
	
	\resumeItemListStart
	\resumeListItem {Developed front-end and back-end components of cloud-based enterprise SaaS product for process data transfers.}
	\resumeListItem {Developed secure RESTful APIs. Did threat modeling of cloud services and corresponding on-prem components.}
	\resumeListItem {Architected and developed an alarm infrastructure and a cloud-based software delivery and auto-update system.}
	\resumeListItem {Enhanced SQL database schema and developed full stack from server-side data-access layer to client-side APIs.}
	\resumeListItem {Developed DevOps tools and data-mining queries for reporting on health statuses of multi-tenant cloud application.}
	\resumeListItem {Developed multi-layered modular and scalable WPF applications.}
	\resumeListItem {Consistently delivered committed items in fast-paced, quick turn-around, scrum-based development cycles. Led knowledge transfer sessions to handover work to new team member(s) while transitioning to a R\&D project.}
	\resumeItemListEnd

	\experienceSubItem{Middleware Box Product}{May 2011 - Feb 2013}
	
	\resumeItemListStart
	\resumeListItem {Developed and maintained native/managed test automation frameworks. \ Developed and maintained software delivery systems using Wise and WiX. Enhanced and maintained codebase (specifically data buffering) for core middleware.}
	\resumeItemListEnd
	
	\experienceItem{QA Engineer}{OSIsoft, LLC., San Leandro, CA}{July 2008 -- April 2011}	
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Architected and developed (automated) test systems for multiple products, reducing release cycle testing time, using C++, .NET, SQL, test automation tools like SilkTest and OOP based UI automation tools.}
	\resumeListItem {Worked with senior developers on middleware code for core product.}
	\resumeItemListEnd
	
	\experienceItem{Engineer, Rotational Engineering Program}{OSIsoft, LLC., San Leandro, CA}{July 2007 -- June 2008}
	\vspace{-8pt}	
	\resumeItemListStart
	\resumeListItem {Resolved OSIsoft PI software issues and went on site visits to configure and troubleshoot PI Software.}
	\resumeListItem {Improved effectiveness of software health metrics by 92\%. Delivered proof-of-concept projects that led to new sales.}
	\resumeListItem {Developed automated test frameworks.}
	\resumeItemListEnd
	
	\experienceItem{Graduate Teaching Assistant}{ECE Dept., NCSU, Raleigh, NC}{Jan 2007 -- May 2007}
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Graded assignments, administered website, answered questions and was instructor for semester project related classes in a controls course.}
	\resumeItemListEnd
	
	\experienceItem{Graduate Research Assistant, ADAC Lab}{ECE Dept., NCSU, Raleigh, NC}{Aug 2006 -- Dec 2006}
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Surveyed publications, wrote portions of research project proposals and reviewed IEEE proceeding submissions.}
	\resumeListItem {Mathematically modeled and simulated a formation controller for mobile robots over a wireless network.}
	\resumeItemListEnd
	
	\experienceItem{Summer Session Teaching Assistant, ADAC Lab}{ECE Dept., NCSU, Raleigh, NC}{May 2006 -- July 2006}
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Developed an embedded micro-controller software library and maintained a slew of mobile robots.}
	\resumeListItem {Supervised, mentored and graded students for term projects in programming, mechatronics, controls.}
	\resumeListItem {Created new labs and instructed a class of 85 students for experiments in a mechatronics graduate level course.}
	\resumeItemListEnd
	
	\experienceItem{Specialist Customer Support}{IBM, Daksh e-Services Private Limited, India}{Jan 2005 -- March 2005}
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Resolved broadband internet connectivity issues with overseas customers.}
	\resumeListItem {Worked with real-time databases to update connectivity status.}
	\resumeItemListEnd
	
	\experienceItem{Summer Intern, Control and Instrumentation}{NEEPCO, AGBPP, India}{July 2003 -- Aug 2003}
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Involved in upgrade of a 33.5 MW turbine-generator control unit at NEEPCO, a \$35 billion power company.}
	\resumeListItem {Obtained field experience in power systems, generation, electrical machines.}
	\resumeItemListEnd

	%-----------Publications-----------------
	\section{Publications}
	
	\resumeItemListStart
	\resumeListItem {R. Vanijjirattikhan, M. Talukdar, and M-Y. Chow, ``Accumulated Effect Parameter Tuning Method for Geometrical Path Tracking of Wheeled Mobile Robots'', \textit{in the proceedings of the IEEE/ASME International Conference on Advanced Intelligent Mechatronics}, Zurich, September 2007.}
	\resumeItemListEnd

	%-----------Skills-----------------
	\section{Skills}

	\textbf{Management}\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem{Project backlog management, requirements analysis, collaborating with customers,  product management, customer support, QA.}
	\resumeListItem {People management, regular 1-1s, performance reviews, career progression mentoring, performance improvement plans, recruiting and on-boarding developers.}
	\resumeItemListEnd

	\textbf{Computing}\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {SaaS, IoT, distributed systems, cloud computing, micro-services, service-oriented architecture, developing APIs, web services, multi-threading, data modeling, software threat modeling, Agile methodology.}
	\resumeListItem {Algorithms, data structures, machine learning (basic), design patterns, system design.}
	\resumeListItem {.NET (C\#), Java, C++ (previous exp.), JavaScript, SQL, NoSQL.}
	\resumeListItem {Azure (Service Fabric, DocumentDB, AppInsights, Redis Cache, etc.), REST, Git, WiX toolset, WPF, MVVM, MVC, ASP.NET, AngularJs.}
	\resumeListItem {OSIsoft PI software}
	\resumeItemListEnd

	\textbf{Languages:} Fluent in Hindi, Assamese (North East Indian language). Elementary Bengali. Basic Sanskrit.
	
	%-----------Additional-----------------
	\section{Additional}
	
	\resumeItemListStart
	\resumeListItem {Successfully completed a 5-year diploma from \textbf{Assam Fine Arts and Crafts Society}, India.}
	\resumeListItem {Performance in Science and Mathematics in All India Secondary School Examination in the top 1/8th.}
	\resumeListItem {Successfully qualified in All-India Mathematics Olympiad conducted by Delhi Association of Mathematics Teachers.}
	\resumeItemListEnd
	

	%-------------------------------------------
\end{document}
