\documentclass[letterpaper,10pt]{article}

\usepackage[english]{babel}
%\usepackage[T1]{fontenc} % needed for pipe character
\usepackage[empty]{fullpage}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[margin=0.5in]{geometry} % setting margins
\usepackage{lmodern} % font
\usepackage{fontawesome}
\usepackage{titlesec} % section formatting
\usepackage[usenames,dvipsnames]{color} % section formatting
%\usepackage{pgffor}
%\usepackage{xifthen}
\usepackage{xparse}
\usepackage{bookmark}

% https://latex.org/forum/viewtopic.php?t=5842
\hyphenpenalty 10000
\exhyphenpenalty 10000

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\title{Manas Talukdar}
\author{Manas Talukdar}
\date{\today}

%\hypersetup{
%	colorlinks=true,
%	linkcolor=blue,
%	filecolor=magenta,  
%	urlcolor=cyan,   
%%	urlcolor=[rgb]{0.0, 0.5, 1.0}, % http://latexcolor.com/
%}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\fancyfoot[C, C]{
	\begin{tabular}{c | c}
		Manas Talukdar\enspace & \enspace \thepage \\
	\end{tabular}
}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\NewDocumentCommand{\educationItem}{mmmom}{
	\IfNoValueTF{#4}
		{ \textbf{#1}, #2, \textit{#3} & #5 \\ }
		{ \textbf{#1}, #2, \textit{#3}, {\small #4} & #5 \\ }
}

\newcommand{\experienceItem}[3]{
	\begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}}c}
		\multicolumn{1}{l}{\textbf{#1}, #2} & \multicolumn{1}{r}{#3}\\
	\end{tabular*}\vspace{-10pt}
}

\ExplSyntaxOn
\NewDocumentCommand{\experienceSubItem}{mmo}{
	\tl_if_empty:nTF{#2} 
		{
			\IfNoValueTF{#3} 
				{ \textit{#1}\vspace{-8pt} }
				{ \textit{#1\enspace[\href{#3}{#3}]}\vspace{-8pt} }
		}
		{
			\IfNoValueTF{#3} 
				{ \textit{#1\enspace(#2)}\vspace{-8pt} }
				{ \textit{#1\enspace(#2)\enspace[\href{#3}{#3}]}\vspace{-8pt} }
		}
}
\ExplSyntaxOff

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeListItem}[1]{
	\item{#1 \vspace{-6pt}}
}

%-------------------------------------------
%%%%%%  Resume content starts here  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}\thispagestyle{empty}
	
		%----------Heading-----------------
	\input{Heading}
	
	%-----------Summary-----------------
	\input{Summary}
	
	%-----------Education-----------------
	\section{Education}	
	
	\input{Education}

	%-----------Recent Experience-----------------
	\section{Recent Experience}
	
	\experienceItem{Software Engineering Team Leader}{OSIsoft, LLC., San Leandro, CA}{Jan 2016 -- present}

	\experienceSubItem{IoT Product}{May 2017 - present}
	
	\resumeItemListStart
	\resumeListItem {Started new team/project on enterprise wide IoT data collection. Interviewed candidates for hiring into the team. Gathered requirements and defined product direction in collaboration with product management and group lead.}
	\resumeListItem {Migrated legacy source control to Git. Developed an administration API with back-end and front-end. Developed a logging infrastructure. Developed mechanism for data egress from IoT module to enterprise storage solutions.}
	\resumeItemListEnd

	\experienceSubItem{SaaS Product}{Jan 2016 - April 2017}[https://bit.ly/2HUbQKb]
	
	\resumeItemListStart
	\resumeListItem {Managed (using Agile processes) a team of software developers working on distributed enterprise scale SaaS product.}
	\resumeListItem {Defined system architecture for a distributed sequential data store to process billions of streams. Collaborated with customers, product managers to identify requirements and develop road-map. Managed SDLC. Introduced CI. Researched new partner technologies and provided feedback [\href{https://bit.ly/2Hy2gfU}{bit.ly/2Hy2gfU}]. Presented at meetings and conferences.}
	\resumeListItem {Recruited and on-boarded developers into team. Assisted team members with sprint tasks and helped them complete goals. Developed a caching service - passed on to developers in the team.}
	\resumeItemListEnd

	\experienceItem{Senior Software Developer}{OSIsoft, LLC., San Leandro, CA}{Feb 2015 -- Jan 2016}
	
	\experienceSubItem{SaaS Product}{}[https://bit.ly/2HUbQKb]
	
	\resumeItemListStart
	\resumeListItem {Architected and developed distributed micro-services using new cloud technology -- Service Fabric [\href{https://bit.ly/2r5hSxY}{bit.ly/2r5hSxY}].}
	\resumeListItem {Security champion for team. Threat modeled components and data flow in the project and led review sessions.}
	\resumeListItem {Architected full-stack real-time health monitoring and logging system with data access and client APIs.}
	\resumeListItem {Interviewed, on-boarded and mentored new engineers in project.}
	\resumeItemListEnd

	\experienceItem{Software Developer}{OSIsoft, LLC., San Leandro, CA}{May 2011 -- Jan 2015}
	
	\experienceSubItem{SaaS R\&D Project}{June 2014 - Jan 2015}[https://bit.ly/2HUbQKb]

	\resumeItemListStart
	\resumeListItem {Developed components of multi-tenant SaaS product for process data storage. Added data replication. Developed automated multi-threaded chaos tests. Developed, documented standards for DevOps -  passed on to other engineers.}
	\resumeListItem {Mentored new engineer in developing a real-time health monitoring framework.}
	\resumeItemListEnd

	\experienceSubItem{SaaS Product}{Feb 2013 - June 2014}[https://bit.ly/2r4i9jV]
	
	\resumeItemListStart
	\resumeListItem {Developed front-end and back-end components of cloud-based enterprise SaaS product for process data transfers.}
	\resumeListItem {Developed secure RESTful APIs. Did threat modeling of cloud services and corresponding on-prem components.}
	\resumeListItem {Architected and developed an alarm infrastructure and a cloud-based software delivery and auto-update system.}
	\resumeListItem {Enhanced SQL database schema and developed full stack from server-side data-access layer to client-side APIs.}
	\resumeListItem {Developed DevOps tools and data-mining queries for reporting on health statuses of multi-tenant cloud application.}
	\resumeListItem {Developed multi-layered modular and scalable WPF applications.}
	\resumeListItem {Consistently delivered committed items in fast-paced, quick turn-around, scrum-based development cycles. Led knowledge transfer sessions to handover work to new team member(s) while transitioning to a R\&D project.}
	\resumeItemListEnd

	\experienceSubItem{Middleware Box Product}{May 2011 - Feb 2013}
	
	\resumeItemListStart
	\resumeListItem {Developed and maintained native/managed test automation frameworks. \ Developed and maintained software delivery systems using Wise and WiX. Enhanced and maintained codebase (specifically data buffering) for core middleware.}
	\resumeItemListEnd

	%-----------Prior Experience-----------------
	\section{Prior Experience}
	
	\experienceItem{QA Engineer}{OSIsoft, LLC., San Leandro, CA}{July 2008 -- April 2011}	
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Architected and developed (automated) test systems for multiple products, reducing release cycle testing time, using C++, .NET, SQL, test automation tools like SilkTest and OOP based UI automation tools.}
	\resumeListItem {Worked with senior developers on middleware code for core product.}
	\resumeItemListEnd
	
	\experienceItem{Engineer, Rotational Engineering Program}{OSIsoft, LLC., San Leandro, CA}{July 2007 -- June 2008}
	\vspace{-8pt}	
	\resumeItemListStart
	\resumeListItem {Resolved OSIsoft PI software issues and went on site visits to configure and troubleshoot PI Software.}
	\resumeListItem {Improved effectiveness of software health metrics by 92\%. Delivered proof-of-concept projects that led to new sales.}
	\resumeListItem {Developed automated test frameworks.}
	\resumeItemListEnd
	
	\experienceItem{Graduate Research/Teaching Assistant}{ECE Dept., NCSU, Raleigh, NC}{May 2006 -- May 2007}
	\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {Wrote research proposals, research project on multi-agent formation controller, created and graded labs and taught some classes as TA for mechatronics and controls courses.}
	\resumeItemListEnd
	
	\experienceItem{Specialist Customer Support}{IBM, Daksh e-Services Private Limited, India}{Jan 2005 -- March 2005}
	
	\experienceItem{Summer Intern, Control and Instrumentation}{NEEPCO, AGBPP, India}{July 2003 -- Aug 2003}

	%-----------Publications-----------------
	\section{Publications}
	
	\resumeItemListStart
	\resumeListItem {R. Vanijjirattikhan, M. Talukdar, and M-Y. Chow, ``Accumulated Effect Parameter Tuning Method for Geometrical Path Tracking of Wheeled Mobile Robots'', \textit{in the proceedings of the IEEE/ASME International Conference on Advanced Intelligent Mechatronics}, Zurich, September 2007.}
	\resumeItemListEnd

	%-----------Skills-----------------
	\section{Skills}

	\textbf{Management}\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem{Project backlog management, requirements analysis, collaborating with customers, product management, support.}
	\resumeListItem {People management, regular 1-1s, performance reviews, career progression mentoring, performance improvement plans, recruiting and on-boarding developers.}
	\resumeItemListEnd

	\textbf{Computing}\vspace{-8pt}
	\resumeItemListStart
	\resumeListItem {SaaS, IoT, distributed systems, cloud computing, micro-services, service-oriented architecture, developing APIs, web services, multi-threading, data modeling, software threat modeling, Agile methodology.}
	\resumeListItem {Algorithms, data structures, machine learning (basic), design patterns, system design.}
	\resumeListItem {.NET (C\#), Java, C++ (previous exp.), JavaScript, SQL, NoSQL.}
	\resumeListItem {Azure (Service Fabric, DocumentDB, AppInsights, Redis Cache, etc.), REST, Git, WiX toolset, WPF, MVVM, MVC, ASP.NET, Angular.}
	\resumeItemListEnd

	\textbf{Languages:} Fluent in Hindi, Assamese (North East Indian language). Elementary Bengali. Basic Sanskrit.

	\textbf{Assam Fine Arts and Crafts Society}, India, 5-year diploma in Fine Arts and Crafts.

	%-------------------------------------------
\end{document}
