% Copyright (c) 2024 Manas Talukdar
% 
% This software is released under the MIT License.
% https://opensource.org/licenses/MIT

\textbf{Professional Memberships and Affiliations}\vspace{-6pt}
\resumeItemListStart
\resumeListItem {Senior member of \href{https://www.ieee.org}{IEEE}.}
\resumeListItem {Member of the \href{https://www.technologyreview.com}{MIT Technology Review} Global Insights Panel.}
\resumeListItem {Member of the \href{https://hbr.org}{[Harvard Business Review} Advisory Council.}
\resumeListItem {Member of the \href{https://www.aiacceleratorinstitute.com}{[AI Accelerator Institute}.}
\resumeListItem {Member and Ambassador at the \href{https://aifn.co/}{AI Frontier Network}.}
\resumeItemListEnd

\textbf{Fellowships}\vspace{-6pt}
\resumeItemListStart
\resumeListItem {Senior Fellow of \href{https://www.ai2030.org/}{AI 2030}.}
\resumeItemListEnd

\textbf{Board Memberships}\vspace{-6pt}
\resumeItemListStart
\resumeListItem {Advisory Board member of \href{https://www.ai2030.org/}{AI 2030}.}
\resumeItemListEnd

\textbf{Judging Roles}\vspace{-6pt}
\resumeItemListStart
\resumeListItem {Judge for Globee Awards.}
\resumeListItem {Judge for \href{https://stevieawards.com/ABA}{American Business Awards} (part of the Stevie Awards).}
\resumeListItem {Accepted as judge for \href{https://www.titanawards.com/}{Titan Business Awards}.}
\resumeListItem {Accepted as judge for \href{https://siia.net/codie/}{2024 SIIA CODiE Awards}.}
\resumeItemListEnd

\textbf{Editor and Reviewer Roles}\vspace{-6pt}
\resumeItemListStart
\resumeListItem {Technical Editor and Reviewer for \href{https://www.manning.com}{Manning Publications}.}
\resumeItemListEnd

\textbf{Advisory Roles}\vspace{-6pt}
\resumeItemListStart
\resumeListItem {Mentor/Advisor for startups at \href{https://www.alchemistaccelerator.com}{Alchemist Accelerator}, a venture backed accelerator for early-stage startups that monetize from enterprises.}
\resumeListItem {Engineering leadership mentor at \href{https://www.platohq.com/@manas-talukdar-zfyuvrxm6if}{Plato}.}
\resumeListItem {AI/ML, career development, technology and leadership mentor at \href{https://mentorcruise.com/mentor/manastalukdar/}{MentorCruise}.}
\resumeListItem {Technology advisor for AI, ML, distributed systems, etc. at \href{https://www.guidepoint.com}{Guidepoint}, \href{https://officehours.com/}{Office Hours}, \href{https://capvision.com}{Capvision}.}
\resumeItemListEnd

\textbf{Speaking Engagements}\vspace{-6pt}
\resumeItemListStart
\resumeListItem {Frequent speaker at engineering and leadership conferences on AI, Data, etc.}
\resumeListItem {Often lead or participate in roundtables and panel discussions.}
\resumeListItem {Delivered graduation speech on AI at university commencement ceremonies.}
\resumeItemListEnd