\textbf{Management}\vspace{-8pt}
\resumeItemListStart
\resumeListItem{Backlog management, requirements analysis, collaborating with customers,  product management, support, etc.}
\resumeListItem {People management, regular 1-1s, performance reviews, career progression mentoring, performance improvement plans, recruiting and on-boarding developers.}
\resumeItemListEnd

\textbf{Computing}\vspace{-8pt}
\resumeItemListStart
\resumeListItem {SaaS, distributed systems, cloud computing, micro-services, IoT, service-oriented architecture, developing APIs, web services, multi-threading, data modeling, software threat modeling, Agile methodology (scrum, kanban).}
\resumeListItem {Algorithms, data structures, machine learning (basic), design patterns, system design.}
% different from Skills
\resumeListItem {\textbf{Languages:}.NET (C\#), Java, Python (basic), JavaScript, C++ (previous exp.).}
\resumeListItem {SQL, NoSQL, REST, MVVM, MVC.}
\resumeListItem {\textbf{Tools and Frameworks:} Angular, Vue.js, Node.js (basic), ASP.NET, WPF, WiX toolset, Git, OSIsoft PI.}
\resumeListItem {\textbf{Microsoft Azure:} Service Fabric, AppInsights, Event Hubs, Blobs, IoT, VMs, DevOps, etc.}
\resumeListItem {\textbf{Amazon Web Services (AWS):} S3, CloudFront, Snowball, IAM, EC2, CloudWatch, RDS, DynamoDB, Redshift, Aurora, Elasticache, RouteS3, VPC (Direct Connect), CloudFormation, Elastic Beanstack, AutoScaling, SQS, SWF, SNS, Elastic Transcoder, API Gateway, Kinesis, Cognito, Lambda, etc.}
% difference ends here
\resumeItemListEnd

\textbf{Languages:} Fluent in Hindi, Assamese (North East Indian language). Elementary Bengali. Basic Sanskrit.