\textbf{Management}\vspace{-8pt}
\resumeItemListStart
\resumeListItem{Organizational growth, engineering productivity.}
\resumeListItem{Agile methodologies (scrum, kanban), backlog management, requirements analysis, collaborating with users,  product, services, support, etc.}
\resumeListItem {People management, 1-1s, performance reviews, career development, performance improvement plans, on-boarding.}
\resumeItemListEnd

\textbf{Computing}\vspace{-8pt}
\resumeItemListStart
\resumeListItem {PaaS, SaaS, distributed systems, cloud computing, data infrastructure, machine learning, micro-services, IoT, APIs, multi-threading, service-oriented architecture, web services, data modeling, software threat modeling.}
\resumeListItem {Data structures, algorithms, design patterns, systems design.}

\resumeListItem {\textbf{Languages:} \underline{Very comfortable}: Java, C\#. \underline{Comfortable}: Python, JavaScript, TypeScript. \underline{Learning}: Go. \underline{Academics, early career}: C/C++, SQL.}
\resumeListItem {\textbf{Data Infrastructure:} SQL, NoSQL, OSIsoft PI.}
\resumeListItem {\textbf{Architectural Constructs:} REST, MVVM, MVC.}
\resumeListItem {\textbf{Frameworks:} Angular, Vue.js, Reactjs. Node.js, .NET, ASP.NET, WPF, WiX toolset.}
\resumeListItem {\textbf{Tools:} VSCode, Visual Studio, IntelliJ, Jira, Confluence.}
\resumeListItem {\textbf{Systems:} Git.}
%\resumeListItem {\textbf{AI and ML:} Neural Networks, TensorFlow, PyTorch.}
\resumeListItem {\textbf{Microsoft Azure:} Service Fabric, AppInsights, Event Hubs, Blobs, IoT, VMs, DevOps, etc.}
\resumeListItem {\textbf{Amazon Web Services (AWS):} S3, IAM, EC2, RDS, DynamoDB, EMR, AutoScaling, SQS, SNS, API Gateway, Lambda, etc.}

\resumeItemListEnd

\input{Languages}
\vspace{-5pt}