{\fontfamily{lmss}\selectfont
	\begin{justify}\textit{Software engineering leader, experienced in building teams and growing organizations. Developed successful cross-departmental strategies to scale multiple software teams across organization. More than 13 years of hands-on industry experience, including as development lead and product owner. Skilled in Agile methodologies, measuring and improving engineering productivity. Experienced in hiring and mentoring engineers, identifying and developing leaders. Excellent communication skills. Successful collaborations with cross-functional stakeholders, including users, executives, product management, services and support. Gathered requirements, identified new product opportunities, managed backlogs and road-maps. Drove adoption across multiple releases. Instituted best practices and processes to streamline rapid growth across multiple teams. Quick learner, self-driven with proven track record in delivering projects that involved learning new technologies. Significant experience in cloud computing, distributed systems and data infrastructure. Recent focus includes real-time, high-throughput streaming data and scalable AI, ML platforms. Current core competencies in large-scale systems design, people, project management and organizational growth.}\end{justify}
	
	\begin{justify}\textit{Trained in management methodologies from UC Berkeley Center for Executive Education.}\end{justify}
	
	\begin{justify}\textit{As Software Engineer, developed on-prem middleware as well as large enterprise scale, multi-tenant, distributed, micro-services based cloud applications. Developed both front-end UI and back-end infrastructure for PaaS and SaaS products, with focus on back-end. Architected and developed several automated product test, release and delivery systems.}\end{justify}

	\begin{justify}\textit{Academic experience in mathematical modeling and simulation of control systems, robotics, neural networks.}\end{justify}

	\begin{justify}\textit{Generally inquisitive about technology and love to work on challenging problems.}\end{justify}
}
\vspace{-12pt}