\experienceItem{Engineering Manager}{C3 AI, Redwood City, CA}{Jan 2020 -- present}

\experienceSubItem{Data Infrastructure, AI/ML Platform}{Jan 2020 - present}

\resumeItemListStart
\resumeListItem {Managing a group of 3 teams building multi-cloud, distributed data infrastructure Platform-as-a-Service (Paas) for large-scale AI/ML applications.}
\resumeListItem{Responsible for key initiatives to deliver major high-visibility features.}
\resumeListItem{Led performance benchmarking initiative against industry solution(s).}
\resumeListItem {Established the Data group within Platform. Grew a team of 6 to a group of \char`\~20 engineers across 3 teams. Defined charter for each team. Identified, mentored and promoted senior engineers to lead roles for each team. Continuing to drive further growth across organization. Established a new interviewing framework. Worked with Talent Acquisition to streamline hiring process.}
\resumeListItem {As part of org leadership refined expected signals and attributes for each role and level in individual contributor track. Instituted a framework for promoting engineers, specially to lead role.}
\resumeListItem{Started data-driven performance analysis across org for developers and teams, mining data from Jira, GitHub, Git, etc. Instituted a 360\textsuperscript{o} feedback framework.}
\resumeListItem{Started a regular Lunch and Learn initiative across org for knowledge sharing and translation of tribal knowledge into technical documentation.}
\resumeItemListEnd