\input{./../PackagesFormattingMetadata}

%-------------------------
% Custom commands

\NewDocumentCommand{\educationItem}{mmmom}{
	\IfNoValueTF{#4}
		{ \textbf{#1}, #2, \textit{#3} & #5 \\ }
		{ \textbf{#1}, #2, \textit{#3}, {\small #4} & #5 \\ }
}

\newcommand{\experienceItem}[3]{
	\begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}}c}
		\multicolumn{1}{l}{\textbf{#1}, #2} & \multicolumn{1}{r}{#3}\\
	\end{tabular*}\vspace{-10pt}
}

\ExplSyntaxOn
\NewDocumentCommand{\experienceSubItem}{mmmo}{ % name, technologies, time-range, link
	\tl_if_empty:nTF{#3} 
	{
		\IfNoValueTF{#4} 
			{ \textit{#1\enspace(#2)}\vspace{-8pt} }
			{ \textit{#1\enspace(#2)\enspace[\href{#4}{#4}]}\vspace{-8pt} }
	}
	{
		\IfNoValueTF{#4} 
			{ \textit{#1\enspace(#2)\enspace(#3)}\vspace{-8pt} }
			{ \textit{#1\enspace(#2)\enspace(#3)\enspace[\href{#4}{#4}]}\vspace{-8pt} }
	}
}
\ExplSyntaxOff

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeListItem}[1]{
	\item{#1 \vspace{-6pt}}
}

%-------------------------------------------
%%%%%%  Resume content starts here  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}\thispagestyle{empty}
	
		%----------Heading-----------------
	\input{./../Heading}
	
	%-----------Summary-----------------
	\input{./../Summary}
	
	%-----------Education-----------------
	\section{Education}	
	
	\input{./../Education}

	%-----------Recent Experience-----------------
	\section{Recent Experience}
	
	\experienceItem{Software Engineering Team Leader}{OSIsoft, LLC., San Leandro, CA}{Jan 2016 -- present}

	\experienceSubItem{IoT Product}{.net core, C\#, docker, reactive programming, Azure, Angular, REST APIs}{}%May 2017 - present
	
	\resumeItemListStart
	\resumeListItem {Started new team/project on enterprise wide IoT data collection. Interviewed candidates for hiring into the team. Gathered requirements and defined product direction in collaboration with product management and group lead.}
	\resumeListItem {Migrated legacy source control to Git. Developed an administration API with back-end and front-end. Developed a logging infrastructure. Developed mechanism for data egress from IoT module to enterprise storage solutions.}
	\resumeItemListEnd

	\experienceSubItem{SaaS Product}{.net core, C\#, Azure, sql, nosql, micro-services, REST APIs}{}[https://bit.ly/2HUbQKb]%Jan 2016 - April 2017
	
	\resumeItemListStart
	\resumeListItem {Managed (using Agile processes) a team of software developers working on distributed enterprise scale SaaS product.}
	\resumeListItem {Defined system architecture for a distributed sequential data store to process billions of streams. Collaborated with customers, product managers to identify requirements and develop road-map. Managed SDLC. Introduced CI. Researched new partner technologies and provided feedback [\href{https://bit.ly/2Hy2gfU}{bit.ly/2Hy2gfU}]. Presented at meetings and conferences.}
	\resumeListItem {Recruited and on-boarded developers into team. Assisted team members with sprint tasks and helped them complete goals. Developed a caching service - passed on to developers in the team.}
	\resumeItemListEnd

	\experienceItem{Senior Software Developer}{OSIsoft, LLC., San Leandro, CA}{Feb 2015 -- Jan 2016}
	
	\experienceSubItem{SaaS Product}{.net, C\#, Azure, micro-services, REST APIs, Angular}{}[https://bit.ly/2HUbQKb]
	
	\resumeItemListStart
	\resumeListItem {Architected and developed distributed micro-services using new cloud technology -- Service Fabric [\href{https://bit.ly/2r5hSxY}{bit.ly/2r5hSxY}].}
	\resumeListItem {Security champion for team. Threat modeled components and data flow in the project and led review sessions.}
	\resumeListItem {Architected full-stack real-time health monitoring and logging system with data access and client APIs.}
	\resumeListItem {Interviewed, on-boarded and mentored new engineers in project.}
	\resumeItemListEnd

	\experienceItem{Software Developer}{OSIsoft, LLC., San Leandro, CA}{May 2011 -- Jan 2015}
	
	\experienceSubItem{SaaS R\&D Project}{.net, C\#, Azure, micro-services}{June 2014 - Jan 2015}[https://bit.ly/2HUbQKb]

	\resumeItemListStart
	\resumeListItem {Developed components of multi-tenant SaaS product for process data storage. Added data replication. Developed automated multi-threaded chaos tests. Developed, documented standards for DevOps -  passed on to other engineers.}
	\resumeListItem {Mentored new engineer in developing a real-time health monitoring framework.}
	\resumeItemListEnd

	\experienceSubItem{SaaS Product}{.net, C\#, Azure, micro-services, REST APIs, SQL, jQuery}{Feb 2013 - June 2014}[https://bit.ly/2r4i9jV]
	
	\resumeItemListStart
	\resumeListItem {Developed front-end and back-end components of cloud-based enterprise SaaS product for process data transfers.}
	\resumeListItem {Developed secure RESTful APIs. Did threat modeling of cloud services and corresponding on-prem components.}
	\resumeListItem {Architected and developed an alarm infrastructure and a cloud-based software delivery and auto-update system.}
	\resumeListItem {Enhanced SQL database schema and developed full stack from server-side data-access layer to client-side APIs.}
	\resumeListItem {Developed DevOps tools and data-mining queries for reporting on health statuses of multi-tenant cloud application.}
	\resumeListItem {Developed multi-layered modular and scalable WPF applications.}
	\resumeListItem {Consistently delivered committed items in fast-paced, quick turn-around, scrum-based development cycles. Led knowledge transfer sessions to handover work to new team member(s) while transitioning to a R\&D project.}
	\resumeItemListEnd

	\experienceSubItem{Middleware Box Product}{C++, .net, C\#, SQL}{May 2011 - Feb 2013}
	
	\resumeItemListStart
	\resumeListItem {Developed and maintained native/managed test automation frameworks. \ Developed and maintained software delivery systems using Wise and WiX. Enhanced and maintained codebase (specifically data buffering) for core middleware.}
	\resumeItemListEnd

	%-----------Prior Experience-----------------
	\section{Prior Experience}
	
	\input{./../Experience/OSIsoft/QaEngineer}
	
	\input{./..//Experience/OSIsoft/Engineer}
	
	\input{./../Experience/NCSU/GraduateRaTa_combined}	
	
	\experienceItem{Specialist Customer Support}{IBM, Daksh e-Services Private Limited, India}{Jan 2005 -- March 2005}
	
	\experienceItem{Summer Intern, Control and Instrumentation}{NEEPCO, AGBPP, India}{July 2003 -- Aug 2003}

	%-----------Publications-----------------
	\section{Publications}
	
	\input{./../Publications}
	
	%-----------Skills-----------------
	\section{Skills}
	
	\input{./../Skills}

	\textbf{Assam Fine Arts and Crafts Society}, India, 5-year diploma in Fine Arts and Crafts.

	%-------------------------------------------
\end{document}
